### 2017-07-26 paper/oopsla17-cameraready/evaluation-user-study.tex
tweak

\mypara{Results}
%
The measured kappa values were $\kappa = 0.68$ for the explanations and
$\kappa = 0.77$ for the fixes; while there is no formal notion for what
consititutes strong agreement~\cite{Krippendorff2012-wd}, kappa values
above $0.60$ are often called ``substantial''
agreement~\cite{Landis1977-ey}.
%
Figure~\ref{fig:results-user-study} summarizes a single annotator's
results, which show that students given \toolname's blame assignment
were generally more likely to correctly explain and fix the type error
than those given \sherrloc's.
%
While there was no discernible difference between \toolname and
\sherrloc for |sepConcat|, \toolname responses for |padZero| and
|mulByDigit| were marked correct 5--30\% more often than the \sherrloc
responses.
%
The results appear to show a trend in favor of \toolname;
%
however, none rise to the level of statistical significance.
%

>>>>

\mypara{Results}
%
The measured kappa values were $\kappa = 0.68$ for the explanations and
$\kappa = 0.77$ for the fixes; while there is no formal notion for what
consititutes strong agreement~\cite{Krippendorff2012-wd}, kappa values
above $0.60$ are often called ``substantial''
agreement~\cite{Landis1977-ey}.
%
Figure~\ref{fig:results-user-study} summarizes a single annotator's
results, which show that students given \toolname's blame assignment
were generally more likely to correctly explain and fix the type error
than those given \sherrloc's.
%
While there was no discernible difference between \toolname and
\sherrloc for |sepConcat|, \toolname responses for |padZero| and
|mulByDigit| were marked correct 5--25\% more often than the \sherrloc
responses.
%
While the results appear to show a trend in favor of \toolname,
they do not rise to the level of statistical significance.
% The results appear to show a trend in favor of \toolname;
% %
% however, none rise to the level of statistical significance.
%
